  % -*- Mode:TeX -*-
%% This file simply contains the commands that actually generate the table of
%% contents and lists of figures and tables.  You can omit any or all of
%% these files by simply taking out the appropriate command.  For more
%% information on these files, see appendix C.3.3 of the LaTeX manual.'

%% Use dense chapters in the toc
\makeatletter
\let\old@chapter\chapter
\def\chapter{\clearpage	% Starts new page.
   \thispagestyle{plain}	% Page style of chapter page is 'plain'
   \@afterindentfalse		% Suppresses indent in first paragraph.  Change
   \secdef\@chapter\@schapter}	% to \@afterindenttrue to have indent.
\let\old@makeschapterhead\@makeschapterhead
\def\@makeschapterhead#1{%
   {\parindent \z@ \raggedright
     \normalfont
     \interlinepenalty\@M
     \Huge \bfseries  #1\par\nobreak
     \vskip 25\p@
   }}
\makeatother

\newcommand\publication[3]{
  \noindent
  \begin{minipage}{\textwidth}
  \textbf{#1} \newline
  \textit{#2} \newline
  #3\par
  \end{minipage}
}

\begin{hyphenrules}{nohyphenation}
  \begin{sloppypar}
    \tableofcontents
    \addtocontents{toc}{\protect\setcounter{tocdepth}{-1}}
    \addcontentsline{toc}{chapter}{Table of Contents}
    \addtocontents{toc}{\protect\setcounter{tocdepth}{2}}
    \newpage
    \listoffigures
    \addcontentsline{toc}{chapter}{List of Figures}
    \newpage
    \listoftables
    \addcontentsline{toc}{chapter}{List of Tables}
    \newpage
    \chapter*{List of Publications}
    \addcontentsline{toc}{chapter}{List of Publications}
      \makeatletter
      \let\old@parskip=\parskip
      \setlength{\parskip}{2em}
      \makeatother

      \publication{Cryogenic Control Architecture for Large-Scale Quantum Computing}
      {J. M. Hornibrook, J. I. Colless, I. D. Conway Lamb, S. J. Pauka, H. Lu, A. C. Gossard, J. D. Watson, G. C. Gardner, S. Fallahi, M. J. Manfra, and D. J. Reilly}
      {\href{https://doi.org/\detokenize{10.1103/PhysRevApplied.3.024010}}{\textcolor{blue}{Phys. Rev. Applied 3, 024010 (2015)}}}

      \publication{An FPGA-based Instrumentation Platform for use at Deep Cryogenic Temperatures}
      {I. D. Conway Lamb, J. I. Colless, J. M. Hornibrook, S. J. Pauka, S. J. Waddy, M. K. Frechtling, and D. J. Reilly}
      {\href{https://doi.org/\detokenize{10.1063/1.4939094}}{\textcolor{blue}{Rev. Sci. Inst. 87, 014701 (2016)}}}

      \publication{On-Chip Microwave Quantum Hall Circulator}
      {A. C. Mahoney, J. I. Colless, S. J. Pauka, J. M. Hornibrook, J. D. Watson, G. C. Gardner, M. J. Manfra, A. C. Doherty, and D. J. Reilly}
      {\href{https://doi.org/\detokenize{10.1103/PhysRevX.7.011007}}{\textcolor{blue}{Phys. Rev. X 7, 011007 (2017)}}}

      \publication{Zero-field Edge Plasmons in a Magnetic Topological Insulator}
      {A. C. Mahoney, J. I. Colless, L. Peeters, S. J. Pauka, E. J. Fox, X. Kou, L. Pan, K. L. Wang, D. Goldhaber-Gordon, and D. J. Reilly}
      {\href{https://doi.org/\detokenize{10.1038/s41467-017-01984-5}}{\textcolor{blue}{Nat. Comms. 8, 1836 (2017)}}}

      \publication{Device Architecture for Coupling Spin Qubits via an Intermediate Quantum State}
      {S. J. Pauka, X. G. Croot, J. D. Watson, G. C. Gardner, S. Fallahi, M. J. Manfra, and D. J. Reilly}
      {\href{https://doi.org/\detokenize{10.1103/PhysRevApplied.10.044058}}{\textcolor{blue}{Phys. Rev. Applied 10, 044058 (2018)}}}

      \publication{Gate-Sensing Charge Pockets in the Semiconductor-Qubit Environment}
      {X. G. Croot, S. J. Pauka, M. C. Jarratt, H. Lu, A. C. Gossard, J. D. Watson, G. C. Gardner, S. Fallahi, M. J. Manfra, and D. J. Reilly}
      {\href{https://doi.org/\detokenize{10.1103/PhysRevApplied.11.064027}}{\textcolor{blue}{Phys. Rev. Applied 11, 064027 (2019)}}}

      \publication{Radio-Frequency Methods for Majorana-Based Quantum Devices: Fast Charge Sensing and Phase-Diagram Mapping}
      {D. Razmadze, D. Sabonis, F. K. Malinowski, G. C. Ménard, S. J. Pauka, H. Nguyen, D. M. T. van Zanten, E. C. T. O'Farrell, J. Suter, P. Krogstrup, F. Kuemmeth, and C. M. Marcus}
      {\href{https://doi.org/\detokenize{10.1103/PhysRevApplied.11.064011}}{\textcolor{blue}{Phys. Rev. Applied 11, 064011 (2019)}}}

      \publication{Characterising Quantum Devices at Scale with Custom Cryo-CMOS}
      {S. J. Pauka, K. Das, J. M. Hornibrook, G. C. Gardner, M. J. Manfra, M. C. Cassidy and D. J. Reilly}
      {\href{https://arxiv.org/abs/1908.07685}{\textcolor{blue}{ar$χ$iv Preprint 1908.07685 (2019)}}}

      \publication{Repairing the Surface of InAs-based Topological Heterostructures}
      {S. J. Pauka, J. D. S. Witt, C. N. Allen, B. Harlech-Jones, A. Jouan, G. C. Gardner, S. Gronin, T. Wang, C. Thomas, M. J. Manfra, D. J. Reilly and M. C. Cassidy}
      {\href{https://arxiv.org/abs/1908.08689}{\textcolor{blue}{ar$χ$iv Preprint 1908.08689 (2019)}}}

      \publication{A Cryogenic Interface for Controlling Many Qubits}
      {S. J. Pauka, K. Das, R. Kalra, A. Moini, Y. Y. Yang, M. Trainer, A. Bousquet, C. Cantaloube, N. Dick, G. C. Gardner, M. J. Manfra and D. J. Reilly}
      {In Preparation (2019)}

      \newpage

      \chapter*{Authorship Attribution Statement}
      \addcontentsline{toc}{chapter}{Authorship Attribution Statement}
      \setlength{\parskip}{1.5em}

      \vspace{-2em}
      \noindent
      Section 2.2 of this thesis is published as J. M. Hornibrook, J. I. Colless, I. D. Conway Lamb, S. J. Pauka, H. Lu, A. C. Gossard, J. D. Watson, G. C. Gardner, S. Fallahi, M. J. Manfra, and D. J. Reilly,
      \textbf{Cryogenic Control Architecture for Large-Scale Quantum Computing},
      \href{https://doi.org/\detokenize{10.1103/PhysRevApplied.3.024010}}{\textcolor{blue}{Phys. Rev. Applied 3, 024010 (2015)}} \\
      I co-designed the study with co-authors, designed, simulated and measured the devices with co-authors, analyzed data with co-authors, and assisted in the drafting of the manuscript.

      \noindent
      Section 3.1 of this thesis is published as A. C. Mahoney, J. I. Colless, S. J. Pauka, J. M. Hornibrook, J. D. Watson, G. C. Gardner, M. J. Manfra, A. C. Doherty, and D. J. Reilly,
      \textbf{On-Chip Microwave Quantum Hall Circulator},
      \href{https://doi.org/\detokenize{10.1103/PhysRevX.7.011007}}{\textcolor{blue}{Phys. Rev. X 7, 011007 (2017)}} \\
      I co-designed the study with co-authors, designed and measured the devices with co-authors, analyzed data with co-authors, performed theoretical analysis, and assisted in the drafting of the manuscript.

      \noindent
      Section 3.2 of this thesis is published as A. C. Mahoney, J. I. Colless, L. Peeters, S. J. Pauka, E. J. Fox, X. Kou, L. Pan, K. L. Wang, D. Goldhaber-Gordon, and D. J. Reilly,
      \textbf{Zero-field Edge Plasmons in a Magnetic Topological Insulator},
      \href{https://doi.org/\detokenize{10.1038/s41467-017-01984-5}}{\textcolor{blue}{Nat. Comms. 8, 1836 (2017)}} \\
      I co-designed the study with co-authors, designed and measured the devices with co-authors, analyzed data with co-authors, and assisted in the drafting of the manuscript.

      \noindent
      Section 4.1 of this thesis is published as S. J. Pauka, X. G. Croot, J. D. Watson, G. C. Gardner, S. Fallahi, M. J. Manfra, and D. J. Reilly,
      \textbf{Device Architecture for Coupling Spin Qubits via an Intermediate Quantum State},
      \href{https://doi.org/\detokenize{10.1103/PhysRevApplied.10.044058}}{\textcolor{blue}{Phys. Rev. Applied 10, 044058 (2018)}} \\
      I co-designed the study with co-authors, designed, fabricated and measured the devices with co-authors, analyzed data with co-authors, and assisted in the drafting of the manuscript.

      \noindent
      Section 4.2 of this thesis is published as X. G. Croot, S. J. Pauka, M. C. Jarratt, H. Lu, A. C. Gossard, J. D. Watson, G. C. Gardner, S. Fallahi, M. J. Manfra, and D. J. Reilly,
      \textbf{Gate-Sensing Charge Pockets in the Semiconductor-Qubit Environment}, \\
      \href{https://doi.org/\detokenize{10.1103/PhysRevApplied.11.064027}}{\textcolor{blue}{Phys. Rev. Applied 11, 064027 (2019)}} \\
      I co-designed the study with co-authors, designed, fabricated and measured the devices with co-authors, analyzed data with co-authors, and assisted in the drafting of the manuscript.

      \noindent
      Section 5.1 of this thesis is published as S. J. Pauka, J. D. S. Witt, C. N. Allen, B. Harlech-Jones, A. Jouan, G. C. Gardner, S. Gronin, T. Wang, C. Thomas, M. J. Manfra, D. J. Reilly and M. C. Cassidy,
      \textbf{Repairing the Surface of InAs-based Topological Heterostructures},
      \href{https://arxiv.org/abs/1908.08689}{\textcolor{blue}{ar$χ$iv Preprint 1908.08689 (2019)}} \\
      I co-designed the study with co-authors, designed, fabricated and measured the devices with co-authors, analyzed data with co-authors, and assisted in the drafting of the manuscript.

      \noindent
      Section 5.2 of this thesis is based on material published in D. Razmadze, D. Sabonis, F. K. Malinowski, G. C. Ménard, S. J. Pauka, H. Nguyen, D. M. T. van Zanten, E. C. T. O'Farrell, J. Suter, P. Krogstrup, F. Kuemmeth, and C. M. Marcus,
      \textbf{Radio-Frequency Methods for Majorana-Based Quantum Devices: Fast Charge Sensing and Phase-Diagram Mapping},
      \href{https://doi.org/\detokenize{10.1103/PhysRevApplied.11.064011}}{\textcolor{blue}{Phys. Rev. Applied 11, 064011 (2019)}} \\
      I co-designed the study with co-authors, measured the devices with co-authors, analyzed data with co-authors, and assisted in the drafting of the manuscript.

      \noindent
      In addition to the statements above, in cases where I am not the corresponding author of a published item, permission to include the published material has been granted by the corresponding author.

      \vspace{2em}
      \hspace*{0mm}Signed:\vspace{2pt}\dashsign\\
      \hspace*{0mm}\phantom{Signed: }Sebastian Pauka\\
      \hspace*{0mm}\phantom{Signed: }Date: 28 Aug 2019

      \noindent
      As supervisor for the candidature upon which this thesis is based, I can confirm that the authorship attribution statements above are correct.

      \vspace{2em}
      \hspace*{0mm}Signed:\vspace{2pt}\dashsign\\
      \hspace*{0mm}\phantom{Signed: }David Reilly\\
      \hspace*{0mm}\phantom{Signed: }Date: 28 Aug 2019

      \makeatletter
      \let\parskip=\old@parskip
      \makeatother
  \end{sloppypar}
\end{hyphenrules}
\newpage\null\newpage

%% Restore chapters starting on left page
\makeatletter
\let\chapter\old@chapter
\let\@makeschapterhead\old@makeschapterhead
\makeatother